---
title: "RGB + MONO Fusion"
author: "jing.tong"
output: html_document
---

```{r, echo=FALSE}
library("EBImage")
  fusion <- function(rgb, mono)
  {
			rgb2y <- 0.299 * imageData(rgb)[,,3] + 0.587 *  imageData(rgb)[,,2] + 0.114 *  imageData(rgb)[,,1]
			rgb2u <- -0.147 * imageData(rgb)[,,3] - 0.289 *  imageData(rgb)[,,2] + 0.436 *  imageData(rgb)[,,1]
			rgb2v <- 0.615 * imageData(rgb)[,,3] - 0.515 *  imageData(rgb)[,,2] - 0.1000 *  imageData(rgb)[,,1]

			rgb2y[rgb2y == 0] <- 1
			
			eps <- 0.000001
			
			ratio <- 1 + ((imageData(mono)[,,1]+eps)/(rgb2y+eps) - 1)/2
			fusiony <- imageData(mono)[,,1]
			fusionu <- rgb2u * ratio
			fusionv <- rgb2v * ratio
			
			out <- rgb

			imageData(out)[,,1] <- fusiony + 2.032 * fusionu
			imageData(out)[,,2] <- fusiony - 0.394  * fusionu - 0.581 * fusionv
			imageData(out)[,,3] <- fusiony + 1.140 * fusionv

			imageData(out)[,,1][imageData(out)[,,1] < 0] <- 0
			imageData(out)[,,1][imageData(out)[,,1] > 1] <- 1
			imageData(out)[,,2][imageData(out)[,,2] < 0] <- 0
			imageData(out)[,,2][imageData(out)[,,2] > 1] <- 1
			imageData(out)[,,3][imageData(out)[,,3] < 0] <- 0
			imageData(out)[,,3][imageData(out)[,,3] > 1] <- 1
			
			return(out)
  }
```

# 1. Introduction
This is an automatic report for RGB & MONO image fusion result. And this report is generated on ```r date()```.

This paper show RGB & MONO image fusion experiment. This step is a component of supernight pipeline.

# 2. Algorithm

The input rgb image is the output of the rgb denoise and mono image is the output of the alignment. We take the following steps to do RGB & MONO image fusion.

* transform rgb image to yuv image.
* replace y channel of rgb image with mono y channel.
* adjust uv channel of rgb according to yrgb/ymono.
* transform fusion yuv image to rgb image.

# 3. Experiment

## 3.1. Fusion with un-denoised rgb image

The following are input rgb image without denoise and mono image.

```{r, echo=FALSE}
  library("EBImage")
  rgb_comp <- readImage("E:/work/R/RGB MONO Fusion/rgb1.jpg")
  mono <- readImage("E:/work/R/RGB MONO Fusion/mono1.jpg")
  input_comb <- combine(rgb_comp, mono)
  display(input_comb, all = TRUE)
  text(x = 20, y = 20, label = "RGB", adj = c(0,1), col = "red", cex = 1)
  text(x = dim(rgb_comp)[1], y = 20, label = "MONO", adj = c(0,1), col = "red", cex = 1)
```

and after our fusion algorithm, we get fusion image.

```{r, echo=FALSE}
  out_comp <- fusion(rgb_comp, mono)
  out_combine <- combine(rgb_comp, out_comp)
  display(out_combine, all = TRUE)
  text(x = 20, y = 20, label = "RGB", adj = c(0,1), col = "red", cex = 1)
  text(x = dim(out_comp)[1], y = 20, label = "Fusion", adj = c(0,1), col = "red", cex = 1)
  writeImage(out_comp, "fusion_1.jpg", quality = 100)
```

It is observed that, without rgb image denoise, the fusion image have many color noise. This may have side-effect for our supernight feature.

## 3.2. Fusion with denoised rgb image

So, we do another experiment. The input rgb image is a denoised image.

```{r, echo=FALSE}
  rgb <- readImage("E:/work/R/RGB MONO Fusion/rgb1_denoise.jpg")
  input_comb <- combine(rgb, mono)
  display(input_comb, all = TRUE)
  text(x = 20, y = 20, label = "RGB", adj = c(0,1), col = "red", cex = 1)
  text(x = dim(rgb)[1], y = 20, label = "MONO", adj = c(0,1), col = "red", cex = 1)
```

and after our fusion algorithm, we get fusion image.

```{r, echo=FALSE}
  out <- fusion(rgb, mono)
  out_combine <- combine(rgb, out)
  display(out_combine, all = TRUE)
  text(x = 20, y = 20, label = "RGB", adj = c(0,1), col = "red", cex = 1)
  text(x = dim(out)[1], y = 20, label = "Fusion", adj = c(0,1), col = "red", cex = 1)
  writeImage(out, "fusion_2.jpg", quality = 100)
```

## 3.3. Two result comparison

Let's compare the different fusion result.

```{r, echo=FALSE}
  comp_combine <- combine(out_comp, out)
  display(comp_combine, all = TRUE)
  text(x = 20, y = 20, label = "Fusion(without rgb denoise)", adj = c(0,1), col = "red", cex = 1)
  text(x = dim(out)[1], y = 20, label = "Fusion(with rgb denoise)", adj = c(0,1), col = "red", cex = 1)
```

For a closer look, we crop a small piece from the image and enlarge it.

```{r, echo=FALSE}
  out_comp_crop <- out_comp[3650:3900, 30:180,]
  out_crop <- out[3650:3900, 30:180,]
  crop_comb <- combine(out_comp_crop, out_crop)
  display(crop_comb, all=TRUE)
  text(x = 20, y = 20, label = "un-denoise", adj = c(0,1), col = "red", cex = 1)
  text(x = dim(out_crop)[1], y = 20, label = "denoise", adj = c(0,1), col = "red", cex = 1)
```

Through Comparative Analysis, we found the fusion image with rgb denoise didn't have color noise anymore, its y channel noise come from mono image. And we will denoise the fusion y channel noise later.
