---
title: "RGB Image Denoise"
author: "jing.tong"
output: html_document
---


```{r, echo=FALSE}
library("EBImage")
  guidedFilter <- function(guide, src, radius, eps)
  {
    #该用box，但是box有问题，效果不对，先用Gaussian走通流程
    w <- makeBrush(size = as.integer(radius),shape='Gaussian', sigma=100)
    
    mean_guide <- filter2(guide, w)
    mean_guide_2 <- mean_guide * mean_guide
    mean_guide2 <- filter2(mean_guide_2, w)
    var_guide <- mean_guide2 - mean_guide * mean_guide
    
    mean_src <- filter2(src, w)
    mean_src_2 <- mean_src * mean_src
    mean_src2 <- filter2(mean_src_2, w)
    cov_src <- mean_src2 - mean_src * mean_src
    
    a <- cov_src/(var_guide + eps)
    b <- mean_guide - a * mean_guide
    
    mean_a <- filter2(a, w)
    mean_b <- filter2(b, w)
    
    return(mean_a * guide + mean_b)
  }
  
  guidedFilterRCaculate <- function(avgLum)
  {
      if (avgLum > 140)
      {
          filterR <- 1;
      }
      else if (avgLum > 120)
      {
          filterR <- 1 + 5 * (140 - avgLum) / 20;
      }
      else if (avgLum > 60)
      {
          filterR <- 5 + 5 * (120 - avgLum) / 60;
      }
      else if (avgLum > 40)
      {
          filterR <- 10 + 25 * (60 - avgLum) / 20;
      }
     else if (avgLum > 20)
      {
          filterR <- 25 + 10 * (40 - avgLum) / 20;
      }
      else if (avgLum >= 0)
      {
          filterR <- 35 + 15 * (20 - avgLum) / 20;
      }
  
      return(filterR);
  }
  
  denoiseColor<- function(input,eps)
  {
    resizeW <- dim(input)[1]/5
    resizeH <- dim(input)[2]/5
    smallImg <- resize(input, w=resizeW, h=resizeH)
    
    avg_b <- mean(imageData(smallImg)[,,1])
    avg_g <- mean(imageData(smallImg)[,,2])
    avg_r <- mean(imageData(smallImg)[,,3])
    avgLum <- (2990 * avg_r + 5870 * avg_g + 1140 * avg_b)/10000
    
    radius <- guidedFilterRCaculate(avgLum)
    
    input <- input/255
    smallOut <- guidedFilter(input, input, radius, eps)
    smallOut <- smallOut * 255
    out <- resize(smallOut, w=dim(input)[1], h=dim(input)[2])
    
    return(out)
    
  }
```

# 1. Introduction

This is an automatic report for RGB image denoise result. And this report is generated on ```r date()```.

This paper show RGB image denoise experiment. This step is a component of supernight pipeline.

# 2. Algorithm

The input images are the output of the alignment. We take the following steps to do RGB image denoise.

* resize RGB image to 1/25 of original size.
* caculate the average luminance of the image.
* caculate the filter radius according to the average luminance.
* blur the image.
* resize the blurred image to original size.

# 3. Experiment

Below, we compared the images before denoise and after denoise.

```{r, echo=FALSE}
  library("EBImage")
  img <- readImage("E:/work/R/RGB Denoise/rgb1.jpg")
  eps <- 0.2
  out <- denoiseColor(img, eps)
  img_comb <- combine(img, out)
  display(img_comb, all=TRUE)
  text(x = 20, y = 20, label = "before", adj = c(0,1), col = "red", cex = 1)
  text(x = dim(img)[1], y = 20, label = "after", adj = c(0,1), col = "red", cex = 1)
  writeImage(out, "rgb_denoise.jpg", quality = 100)
```

For a closer look, we crop a small piece from the image and enlarge it.

```{r, echo=FALSE}
  img_crop <- img[3650:3900, 30:180,]
  out_crop <- out[3650:3900, 30:180,]
  crop_comb <- combine(img_crop, out_crop)
  display(crop_comb, all=TRUE)
  text(x = 20, y = 20, label = "before", adj = c(0,1), col = "red", cex = 1)
  text(x = dim(img_crop)[1], y = 20, label = "after", adj = c(0,1), col = "red", cex = 1)
```

