---
title: "Local Color Correction Using Non-Linear Masking"
author: "jing.tong"
output: html_document
---


```{r, echo=FALSE}
library("EBImage")
  nonLinearMask <- function(input, radius, sig, midtone)
  {
    resizeW <- dim(input)[1]/5
    resizeH <- dim(input)[2]/5
    smallImg <- resize(input, w=resizeW, h=resizeH)
    
    input2y <- 0.299 * imageData(input)[,,3] + 0.587 *  imageData(input)[,,2] + 0.114 *  imageData(input)[,,1]
		input2u <- -0.147 * imageData(input)[,,3] - 0.289 *  imageData(input)[,,2] + 0.436 *  imageData(input)[,,1]
		input2v <- 0.615 * imageData(input)[,,3] - 0.515 *  imageData(input)[,,2] - 0.1000 *  imageData(input)[,,1]
		
		smallImg2y <- 0.299 * imageData(smallImg)[,,3] + 0.587 *  imageData(smallImg)[,,2] + 0.114 *  imageData(smallImg)[,,1]
		
		smallImg2y <- 1.0 - smallImg2y
		
		w <- makeBrush(size = radius,shape='Gaussian', sigma=sig)
		tmpMask <- filter2(smallImg2y, w)
		mask <- resize(tmpMask, w=dim(input)[1], h=dim(input)[2])
		
		out <- input
		exponent <- 2^((midtone - mask) / midtone)
		input2y <- input2y^exponent
		
		imageData(out)[,,1] <- input2y + 2.032 * input2u
		imageData(out)[,,2] <- input2y - 0.394  * input2u - 0.581 * input2v
		imageData(out)[,,3] <- input2y + 1.140 * input2v
    
    return(out)
  }
```

# 1. Introduction

This is an automatic report for RGB image local color correction using non-linear masking result. And this report is generated on ```r date()```.

This paper show RGB image local color correction using non-linear masking experiment. This step is a component of supernight pipeline.

# 2. Algorithm

The input images are the output of the fusion. The following is the block diagram of the algorithm.

```{r, echo=FALSE}
  library("EBImage")
  img <- readImage("E:/work/R/Color Correction/Local1.jpg")
  display(img)
```

The whole algorithm can be divided into two parts:

* calculate an image mask.
* combine the mask and the input image.

## 2.1. Calculate mask

There are several steps to derivate the image mask.

* convert RGB image to gray image.
* invert the gray image.
* blur the inverted image using large radiua filter.

## 2.2. Combination

This step implement by a simple equation.

```{r, echo=FALSE}
  library("EBImage")
  img <- readImage("E:/work/R/Color Correction/Local2.jpg")
  display(img)
```


And a curve can express the relationship between input and output through mask.

```{r, echo=FALSE}
  library("EBImage")
  img <- readImage("E:/work/R/Color Correction/Local3.jpg")
  display(img)
```

# 3. Experiment

Below, we compared the images before correction and after correction.

```{r, echo=FALSE}
  library("EBImage")
  img <- readImage("E:/work/R/Color Correction/fusion2_1.jpg")
  radius <- 15
  sigma <- 9
  midtone <- 0.5
  out <- nonLinearMask(img, radius, sigma, midtone)
  img_comb <- combine(img, out)
  display(img_comb, all=TRUE)
  text(x = 20, y = 20, label = "before", adj = c(0,1), col = "red", cex = 1)
  text(x = dim(img)[1], y = 20, label = "after", adj = c(0,1), col = "red", cex = 1)
  writeImage(out, "colorCorrection.jpg", quality = 100)
```
